### 2020-10-09 introduction.tex
Responded to several TODOs, updated bibliography. Minor additions to introduction.

\begin{document}
\section{Related Work and Conclusion}
\end{document}

>>>>

\begin{document}
\section{Introduction}

Things to discuss in the intro:

\begin{itemize}
\item GV is a session-typed functional language.
\item
  The benefits of using a functional language as opposed to a process calculus are that:
  \begin{itemize}
  \item 
    it supports higher-order functions (and therefore abstraction) not usually present in process calculi; and
  \item
    it allows us to derive extensions of the communication fragment of the language via well-understood extensions of the functional fragment, i.e., deriving internal/external choice from sum types.
  \end{itemize}
\item
  The benefits of using GV over other session-typed functional languages are that:
  \begin{itemize}
  \item
    GV has strong ties to linear logic~\cite{wadler15}.
  \end{itemize}
\item
  Historically, calculi in the GV family~\cite{wadler15,lindley15} have achieved deadlock freedom via a syntactic restriction, i.e., by combining channel creation and thread creation into a single operation, called fork. Unfortunately, this is overly restrictive, as it limits the possible communication structures to trees. The calculus GV is based on, on the other hand, did not satisfy deadlock freedom~\cite{GAY2019}.
\end{itemize}

\begin{itemize}
\item talking about what is GV and its "benefits"
\item next, talking about deadlock freedom property, the benefits and the fact that the original GVs do not satisfy DF
\item in the meantime, in a concurrent setting based on pi-calculus there is a curry-howard correspondence of logic and session typed pi, where DF holds
\item talk about CP here
\item \cite{dardha2018} brought the research fwd and added priorities a la Kobayashi and Padovani to CP, producing PCP
\item following that lead, we present PGV
\item running example of the scheduler in PGV (hopefully)
\item translation of PCP to PGV and what it means to have that.
\item a contribution paragraph with the following
  \begin{itemize}
  \item PGV and what are the benefits
  \item updated PCP
  \item encoding PCP to PGV
  \item technical results to be referred to explicitly
  \end{itemize}
\end{itemize}

\end{document}
